Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-20 eswc-2012/phdsymp.tex
plural
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@110 43ef1190-90fd-4dd7-a769-d0121f02b80e
minor cleanup
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@111 43ef1190-90fd-4dd7-a769-d0121f02b80e

Within the currently published benchmarks, it is up to the user to
select an engine with the best characteristics, relative to their own
expected application. However, I am often asked the question: ``what
is the best general-purpose triple store?'' Those who ask are usually not
prepared to expand on the question. Thus, we should ask ourselves: 
Can we collapse all the metrics into a single \emph{test
  statistic} that can summarize the performance of the engine as a
whole? Also, can we provide a system for developers that they can use
to see if any changes they do to the engine can have unexpected adverse
effects on other parts of the system? For those who are able to
qualify their inquiry, weighing different parts of the system or
metrics is more useful and will yield a more tenable answer, and
motivates the question: Can we use the system to better find the
distinguishing characteristics so that we can return a question that
will actually help new users of SPARQL engines to chose one that meets
their needs?

@@

The problems addressed by existing benchmarks such as the one cited
above are almost orthogonal to the problems considered by my proposed
project. While I have heard of some cases where a hypothesis test is
used to demonstrate that one implementation is better than another, it
seems not to be common practice. Furthermore, I have not to date seen
any work towards using contemporary statistical methods to evaluate
the performance of software, but I shall admit that my literature
study has been limited to RDF/OWL databases, and practical benchmarks
of databases, file systems, scientific software, etc. Therefore, the
existence of relevant references in the deeper computer science
literature is a key issue I would appreciate discussing at the
Symposium.

@@

Factorial design is covered in elementary text-books in
statistics but is most likely inadequate for this purpose, so I intend
to go further into the statistical literature to see if there is a
methodology that is even better suited to the problem. Using
this, I hope to use, amongst other things, the complexity analysis of
SPARQL to find suitable factors to see if my admittedly bold
proposition that it is possible to design a benchmark to cover all
realistic cases can be shown to hold.

>>>>

With the currently published benchmarks, it is up to the user to
select an engine with the best characteristics, relative to their own
expected application. However, I am often asked the question: ``what
is the best general-purpose triple store?'' Those who ask are usually not
prepared to expand on the question. Thus, we should ask ourselves: 
Can we collapse all the metrics into a single \emph{test
  statistic} that can summarize the performance of the engine as a
whole? Also, can we provide a system for developers that they can use
to see if any changes they do to the engine can have unexpected adverse
effects on other parts of the system? For those who are able to
qualify their inquiry, weighing different parts of the system or
metrics is more useful and will yield a more tenable answer, and
motivates the question: Can we use the system to better find the
distinguishing characteristics so that we can return a question that
will actually help new users of SPARQL engines to chose one that meets
their needs?

@@

The problems addressed by existing benchmarks such as the ones cited
above are almost orthogonal to the problems considered by my proposed
project. While I have heard of some cases where a hypothesis test is
used to demonstrate that one implementation is better than another, it
seems not to be common practice. Furthermore, I have not to date seen
any work towards using contemporary statistical methods to evaluate
the performance of software, but I shall admit that my literature
study has been limited to RDF/OWL databases, and practical benchmarks
of databases, file systems, scientific software, etc. Therefore, the
existence of relevant references in the deeper computer science
literature is a key issue I would appreciate discussing at the
Symposium.

@@

Factorial design inspires the present work and is covered in
elementary text-books in statistics but is inadequate for this
purpose, so I intend to go further into the statistical literature to
see if there is a methodology that is better suited to the
problem. Using this, I hope to use, amongst other things, the
complexity analysis of SPARQL to find suitable factors to see if my
admittedly bold proposition that it is possible to design a benchmark
to cover all realistic cases can be shown to hold.
